---
title: "Psoprocessing the JA feature file"
output: html_notebook
---


#Code
In this notebook I'm going to write code for converting the csv files that genetrated in the JA.FeatExtraction.Rmd file and convert it to the final format accroding to the Karen's comments

1- I'm going to merge the "other" or "blinking.OR.not.looking.at.the.display" with less tha 100ms. with the previous lokking area
2- extract number of full and partial joint attention crircles 
```{r Libs}
library(tidyverse)
library(dplyr)
library(ggplot2)
library(skimr)
library(stringr)
```




#Reading the data

```{r Getting all file names}
#"check.names=FALSE" allows to have % in the colnames

#listing all csv files in the path
##the first 5 character of each element in the below lis show the subject ID
filenames.list <- list.files("./Data/NewRawDataExports_06.13.2022/All", pattern="*.csv")

filenames.full.path.list <- list.files("./Data/NewRawDataExports_06.13.2022/All", pattern="*.csv", full.names = TRUE)


```

```{r}
driver.fun()
```


```{r Reading files and applying main functions on them}
driver.fun <- function()
  {
 
  No.of.TAOI <- 7
#total number of subjects (which is the total number of files in the folder)
no.of.JA.files <-
  length(filenames.full.path.list)

#The below df contains six features (looking.area,	 start.time.relative,	 start.time.original	 end.time.relative,	 end.time.original, and	 duration) for each TAOI for all subjects (after merging "other" and "blinking" with <=100ms duration).
#The first column would be the subject ID and the rest are correspond to the features. So the total number of columns would be "6*No.of.TAOI + 1"

#each subject would have 200 rows, so I'm gonna do rbind to add data for each subject to this final df.
final.features.merged.df.4.all.subjects <-
  as.data.frame(matrix(nrow = 1, 
                       ncol = 6*No.of.TAOI + 1))

colnames(final.features.merged.df.4.all.subjects)<- 
  colnames(final.csv.features.merged.4.this.sbj)

#colnames(final.csv.features.merged.4.this.sbj)=========
#  [1] "SubjectID"                                                                            
#  [2] "AOI.hit..BA.Joint.Attention.04.12.2019...04_Box_Target_Box.looking.area"                
#  [3] "AOI.hit..BA.Joint.Attention.04.12.2019...04_Box_Target_Box.start.time.relative"         
#  [4] "AOI.hit..BA.Joint.Attention.04.12.2019...04_Box_Target_Box.start.time.original"         
#  [5] "AOI.hit..BA.Joint.Attention.04.12.2019...04_Box_Target_Box.end.time.relative"           
#  [6] "AOI.hit..BA.Joint.Attention.04.12.2019...04_Box_Target_Box.end.time.original"           
#  [7] "AOI.hit..BA.Joint.Attention.04.12.2019...04_Box_Target_Box.duration"                    
#  [8] "AOI.hit..BA.Joint.Attention.04.12.2019...05_Comb_Target_Comb.looking.area"              
#  [9] "AOI.hit..BA.Joint.Attention.04.12.2019...05_Comb_Target_Comb.start.time.relative"       
# [10] "AOI.hit..BA.Joint.Attention.04.12.2019...05_Comb_Target_Comb.start.time.original"       
# [11] "AOI.hit..BA.Joint.Attention.04.12.2019...05_Comb_Target_Comb.end.time.relative"         
# [12] "AOI.hit..BA.Joint.Attention.04.12.2019...05_Comb_Target_Comb.end.time.original"         
# [13] "AOI.hit..BA.Joint.Attention.04.12.2019...05_Comb_Target_Comb.duration"                  
# [14] "AOI.hit..BA.Joint.Attention.04.12.2019...06_PointyComb_Target_Comb.looking.area"        
# [15] "AOI.hit..BA.Joint.Attention.04.12.2019...06_PointyComb_Target_Comb.start.time.relative" 
# [16] "AOI.hit..BA.Joint.Attention.04.12.2019...06_PointyComb_Target_Comb.start.time.original" 
# [17] "AOI.hit..BA.Joint.Attention.04.12.2019...06_PointyComb_Target_Comb.end.time.relative"   
# [18] "AOI.hit..BA.Joint.Attention.04.12.2019...06_PointyComb_Target_Comb.end.time.original"   
# [19] "AOI.hit..BA.Joint.Attention.04.12.2019...06_PointyComb_Target_Comb.duration"            
# [20] "AOI.hit..BA.Joint.Attention.04.12.2019...08_GreatHair_Target_Teddy.looking.area"        
# [21] "AOI.hit..BA.Joint.Attention.04.12.2019...08_GreatHair_Target_Teddy.start.time.relative" 
# [22] "AOI.hit..BA.Joint.Attention.04.12.2019...08_GreatHair_Target_Teddy.start.time.original" 
# [23] "AOI.hit..BA.Joint.Attention.04.12.2019...08_GreatHair_Target_Teddy.end.time.relative"   
# [24] "AOI.hit..BA.Joint.Attention.04.12.2019...08_GreatHair_Target_Teddy.end.time.original"   
# [25] "AOI.hit..BA.Joint.Attention.04.12.2019...08_GreatHair_Target_Teddy.duration"            
# [26] "AOI.hit..BA.Joint.Attention.04.12.2019...10_Spinner_Target_Spinner.looking.area"        
# [27] "AOI.hit..BA.Joint.Attention.04.12.2019...10_Spinner_Target_Spinner.start.time.relative" 
# [28] "AOI.hit..BA.Joint.Attention.04.12.2019...10_Spinner_Target_Spinner.start.time.original" 
# [29] "AOI.hit..BA.Joint.Attention.04.12.2019...10_Spinner_Target_Spinner.end.time.relative"   
# [30] "AOI.hit..BA.Joint.Attention.04.12.2019...10_Spinner_Target_Spinner.end.time.original"   
# [31] "AOI.hit..BA.Joint.Attention.04.12.2019...10_Spinner_Target_Spinner.duration"            
# [32] "AOI.hit..BA.Joint.Attention.04.12.2019...12_GreatScarf_Target_Scarf.looking.area"       
# [33] "AOI.hit..BA.Joint.Attention.04.12.2019...12_GreatScarf_Target_Scarf.start.time.relative"
# [34] "AOI.hit..BA.Joint.Attention.04.12.2019...12_GreatScarf_Target_Scarf.start.time.original"
# [35] "AOI.hit..BA.Joint.Attention.04.12.2019...12_GreatScarf_Target_Scarf.end.time.relative"  
# [36] "AOI.hit..BA.Joint.Attention.04.12.2019...12_GreatScarf_Target_Scarf.end.time.original"  
# [37] "AOI.hit..BA.Joint.Attention.04.12.2019...12_GreatScarf_Target_Scarf.duration"           
# [38] "AOI.hit..BA.Joint.Attention.04.12.2019...17_LookTruck_Target_Truck.looking.area"        
# [39] "AOI.hit..BA.Joint.Attention.04.12.2019...17_LookTruck_Target_Truck.start.time.relative" 
# [40] "AOI.hit..BA.Joint.Attention.04.12.2019...17_LookTruck_Target_Truck.start.time.original" 
# [41] "AOI.hit..BA.Joint.Attention.04.12.2019...17_LookTruck_Target_Truck.end.time.relative"   
# [42] "AOI.hit..BA.Joint.Attention.04.12.2019...17_LookTruck_Target_Truck.end.time.original"   
# [43] "AOI.hit..BA.Joint.Attention.04.12.2019...17_LookTruck_Target_Truck.duration"
#Rest======

#The below df contains the number of full and partial JA circles for all subjects.
#the first column would be the subject ID and the rest are correspond to number of full/partial JA circles. So the total number of columns would be "2*No.of.TAOI + 1"
ja.full.partial.cricle.count.df.4.all.subjects <-
  as.data.frame(matrix(nrow = no.of.JA.files, 
                       ncol = 2*No.of.TAOI + 1))

loop.index <- 0
#browser() 
for (filenames.full.path in filenames.full.path.list) 
{
  #browser() 
  
  loop.index <- 
    loop.index + 1
  #extracting the subject ID
  SubjectID <- 
    str_sub(filenames.list[[loop.index]],1,5)
  print(">>>><<<< >>>><<<< >>>><<<< >>>><<<< >>>><<<< >>>><<<<")
  print(paste(loop.index, " from ", no.of.JA.files))
  print("^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^")
  final.csv.features.4.this.sbj <- 
    read.csv(file = filenames.full.path, row.names = 1)
  final.csv.features.merged.4.this.sbj <- 
    ja.merge.Other.and.Blinking.less.than.100.ms.(final.csv.features = final.csv.features.4.this.sbj, subjectID = SubjectID)
  

  final.features.merged.df.4.all.subjects <-
    rbind(final.features.merged.df.4.all.subjects , 
          final.csv.features.merged.4.this.sbj)
  #in calling "ja.full.partial.cricle.count" we should drop the first column
  #beacuse it's subject ID and in "ja.full.partial.cricle.count" function the first column is the looking area for the first TAOI
  ja.full.partial.cricle.count.df.4.current.sbj <- 
    ja.full.partial.cricle.count(final.csv.features.merged = final.csv.features.merged.4.this.sbj[,-1], 
                              No.of.TAOI = No.of.TAOI)
 #assigning subject ID for this subject
 ja.full.partial.cricle.count.df.4.current.sbj$SubjectID <- 
    SubjectID
 #adding to the final df 
 ja.full.partial.cricle.count.df.4.all.subjects[loop.index,] <-
   ja.full.partial.cricle.count.df.4.current.sbj
}

#assigning the appropirate col names to the two final dfs
colnames(final.features.merged.df.4.all.subjects) <- 
  colnames(final.csv.features.merged.4.this.sbj)
colnames(ja.full.partial.cricle.count.df.4.all.subjects) <- 
  (colnames(ja.full.partial.cricle.count.df.4.current.sbj))
#removing the first NA row
final.features.merged.df.4.all.subjects <-
  final.features.merged.df.4.all.subjects[-1,]



#writing dfs to HDD=====
relative.folder.path <- 
  "./Data/NewRawDataExports_06.13.2022/All/Subjects.With.ExtractedFeatures/FinalRes/"

file.name <- paste(relative.folder.path, "final.features.merged.df.4.all.subjects.csv", sep = "")
write.csv(final.features.merged.df.4.all.subjects, file = file.name)


file.name <- paste(relative.folder.path, "ja.full.partial.cricle.count.df.4.all.subjects.csv", sep = "")
write.csv(ja.full.partial.cricle.count.df.4.all.subjects, file = file.name)
  


}
```

Merging the "other" and "blinking.OR.not.looking.at.the.display" with less than 100ms. with the previous lokking area

```{r mergeing function defenition}
#INPUT: "final.csv.features" a df that is the output of "ja.Preprocessing.and.FeatureExtraction" which was processed using "write.JA.lookingPatterns2HDD" function. "subjectID": subject ID which is usally the first 5 characters of the file name. 
#OUTPUT: "final.csv.features.merged" the same df that "other" and "blinking.OR.not.looking.at.the.display" with less than 100ms were merged.
ja.merge.Other.and.Blinking.less.than.100.ms. <- function(final.csv.features, subjectID)
{
    #merging "other" and "blinking.OR.not.looking.at.the.display"====
  #below df is a sample df generated in the JA.FeatExtraction.Rmd
  dim(final.csv.features)
  #View(final.csv.features)
  #for each TAOI, we have six different cols: 
  #"looking.area",
  #    "start.time.relative", "start.time.original", 
  #    "end.time.relative", "end.time.original",
  #    "duration"
  #View(final.csv.features)
  
  #Renaming the name of area to make it more simple=====
  final.csv.features[final.csv.features == "Other"] <- 
    "O"
  final.csv.features[final.csv.features == "blinking.OR.not.looking.at.the.display"] <- 
    "B"
  final.csv.features[final.csv.features == "Hand"] <- 
    "H"
  final.csv.features[final.csv.features == "Face"] <- 
    "F"
  final.csv.features[final.csv.features == "TAOI"] <- 
    "T"
  
  for (TAOI.No in c(1:No.of.TAOI)) 
  {
    
    TOA.col.index <-  
      (TAOI.No - 1 ) * 6 + 1 
    No.of.Partial.JA.Circle <- 0 
    No.of.Full.JA.Circle <- 0 
    #browser()
    if (final.csv.features[1,TOA.col.index] == -1) #this TAOI was not hitted
    {
      next()
    }
    
    #calculating the number of rows that we have in the corresponding column for the current TAOI
    no.of.rows <- 
      length(na.omit(final.csv.features[,TOA.col.index]))
    
    #in this loop I'm going to count the "No.of.Partial.JA.Circle" 
    #and "No.of.Full.JA.Circle"
    #So, in each iteration; I should check the three last areas that were hitted
    
    current.row.index <- 2
    while (current.row.index <= (no.of.rows) ) 
    {
      prev.hitted.area <- 
        final.csv.features[(current.row.index - 1),TOA.col.index]
      current.hitted.area <- 
        final.csv.features[current.row.index ,TOA.col.index]
      current.hitted.area.duration <- 
        final.csv.features[current.row.index,TOA.col.index+5]
      
      #if there two consecutive hitted area with the same name (it could happen if in the previous iterations merge happened)
      #Then the two corresponding rwos shold be merged
      should.merge.with.prev.beacuse.the.same.area <- 
        (prev.hitted.area == current.hitted.area)
      
     if (should.merge.with.prev.beacuse.the.same.area) 
      {
        #adding the duration time to the prev. duration time
        final.csv.features[current.row.index - 1,TOA.col.index + 5] <-
          final.csv.features[current.row.index - 1,TOA.col.index + 5] + current.hitted.area.duration
        
        #shifting the rest of the df one row up (just that part of the df that is correspond to the current TAOI)
        final.csv.features[c((current.row.index):(no.of.rows)),c(TOA.col.index : (TOA.col.index + 5))] <- 
          final.csv.features[c((current.row.index+1):(no.of.rows+1)),c(TOA.col.index : (TOA.col.index + 5))]
        #becuse of shifiting the number of non.NA rows decreased by one!
        no.of.rows <-
          no.of.rows - 1
        #because we moved the rows, we shouldn't change the current.row.index. 
        #Now current.row.index shows a new row 
        next()
      }
      #browser()
       #check the merging criteri
      should.merge.with.prev.beacuse.of.short.blinkingORothers <- 
        (current.hitted.area %in% c("B", "O")) & current.hitted.area.duration <= 100
  
      if (should.merge.with.prev.beacuse.of.short.blinkingORothers) 
      {
        #adding the duration time to the prev. duration time
        final.csv.features[current.row.index - 1,TOA.col.index + 5] <-
          final.csv.features[current.row.index - 1,TOA.col.index + 5] + current.hitted.area.duration
        
        #shifting the rest of the df one row up (just that part of the df that is correspond to the current TAOI)
        final.csv.features[c((current.row.index):(no.of.rows)),c(TOA.col.index : (TOA.col.index + 5))] <- 
          final.csv.features[c((current.row.index+1):(no.of.rows+1)),c(TOA.col.index : (TOA.col.index + 5))]
        #becuse of shifiting the number of non.NA rows decreased by one!
        no.of.rows <-
          no.of.rows - 1
        #because we moved the rows, we shouldn't change the current.row.index. 
        #Now current.row.index shows a new row 
        next()
      }
      #update the current.row.index for the nex iteration
      current.row.index <- current.row.index + 1 
    }
    
  }
  sbj.vctr <- 
    rep(subjectID, nrow(final.csv.features))
  final.csv.features.merged<- 
    cbind(SubjectID= sbj.vctr, final.csv.features)
  return(final.csv.features.merged)
}#function

```



```{r counting full/partial function defenition "}

ja.full.partial.cricle.count <- function(final.csv.features.merged, No.of.TAOI)
{
  #browser()
  #for each TAOI, we have six different cols: 
  #"looking.area",
  #    "start.time.relative", "start.time.original", 
  #    "end.time.relative", "end.time.original",
  #    "duration"
  #View(final.csv.features.merged)
  
  #the final df for full/partial JA cricles counts
  #for each TAOI we will compute two numbers for full/partial JA cricles counts
  #the first col would be the sbj ID
  #MANUAL!!!
  no.of.subjects <- 1
  subject.NO <- 1
  ja.cricles.counts.df <-  matrix(nrow = no.of.subjects, 
         ncol = (2*No.of.TAOI +1) )
  ja.cricles.counts.df <- 
    as.data.frame(ja.cricles.counts.df)
  #assigning the colnames
  #seq(2,2*No.of.TAOI,2) is the vector corresponding to the even columns that are supposed to have number of full JA cycles
  #seq(3,2*No.of.TAOI+1,2) is the vector corresponding to the even columns that are supposed to have number of partial JA cycles
  colnames(ja.cricles.counts.df)[seq(2,2*No.of.TAOI,2)] <- 
    paste(TAOI.Target.ColName.Vctr, ".No.of.Full.JA.Cycles", sep = "__")
  colnames(ja.cricles.counts.df)[seq(3,2*No.of.TAOI+1,2)]<- 
    paste(TAOI.Target.ColName.Vctr, ".No.of.Partial.JA.Cycles", sep = "__")
  colnames(ja.cricles.counts.df)[1] <- "SubjectID"
  
  
  #in each iteratoin full/partial JA cricles will be calculated for one TAOI
  
  for (TAOI.No in c(1:No.of.TAOI)) 
  {
    #TAOI.No <- 1
    TOA.col.index <-  
      (TAOI.No - 1 ) * 6 + 1 
    No.of.Partial.JA.Circle <- 0 
    No.of.Full.JA.Circle <- 0 
    
    if (final.csv.features.merged[1,TOA.col.index] == -1) #this TAOI was not hitted
    {
      next()
    }
    
    #calculating the number of rows that we have in the corresponding column for the current TAOI
    no.of.rows <- 
      length(na.omit(final.csv.features.merged[,TOA.col.index]))
    
    #in this loop I'm going to count the "No.of.Partial.JA.Circle" 
    #and "No.of.Full.JA.Circle"
    #So, in each iteration; I should check the three last areas that were hitted
  
    current.row.index <- 1
    while (current.row.index <= (no.of.rows -2) ) 
    {
      first.hitted.area <- 
        final.csv.features.merged[current.row.index,TOA.col.index]
      second.hitted.area <- 
        final.csv.features.merged[current.row.index + 1,TOA.col.index]
      third.hitted.area <- 
        final.csv.features.merged[current.row.index + 2,TOA.col.index]
      
      last.three.looking.are.vctr <- 
        c(first.hitted.area, second.hitted.area, third.hitted.area)
  
      is.Full.JA.Circle <- 
        (sum(last.three.looking.are.vctr == c("T","F","T")) == 3) | (sum(last.three.looking.are.vctr == c("F","T","F")) == 3)
        
      #check for full joint attention
      if (is.Full.JA.Circle) 
      {
        No.of.Full.JA.Circle <- 
          No.of.Full.JA.Circle + 1
        #update the current.row.index for the nex iteration
        #the nex circle can start from  current.row.index + 2  (has overlap with the current one)
        current.row.index <- current.row.index + 2 
        next()
      }
      #The same for partial JA cricle======
      is.Partial.JA.Circle <- 
        (sum(last.three.looking.are.vctr == c("H","F","H")) == 3) |
        (sum(last.three.looking.are.vctr == c("H","T","H")) == 3) |  (sum(last.three.looking.are.vctr == c("F","H","F")) == 3) |  (sum(last.three.looking.are.vctr == c("T","H","T")) == 3)
        
      #check for full joint attention
      if (is.Partial.JA.Circle) 
      {
        No.of.Partial.JA.Circle <- 
          No.of.Partial.JA.Circle + 1
        #update the current.row.index for the nex iteration
        #the nex circle can start from  current.row.index + 2  (has overlap with the current one)
        current.row.index <- current.row.index + 2 
        next()
      }
  
      
      
      #update the current.row.index for the nex iteration
      current.row.index <- current.row.index + 1 
    }
    
    #write the JA.Circles
    ja.cricles.counts.df[subject.NO, TAOI.No*2] <- 
      No.of.Full.JA.Circle
    ja.cricles.counts.df[subject.NO, TAOI.No*2+1] <- 
      No.of.Partial.JA.Circle
        
    
  }
return(ja.cricles.counts.df) 
}
```



#Notes
1- only "Blinking" and "Other" are merged with the prev. looking area if the duration is <100 m.s.
2- if "Blinking" and "Other" are the first area then those are not merging (because there is no prev. area)



```{r add dxj}
#reading the dxj info
dxj.df.4.JA <- read.csv("/Users/apple/Desktop/Eric/Research/Karen/Classifier/Data/MostUpdated/JointAttentionRawData/JA.FeatureExtraction..R.Proj./Data/NewRawDataExports_06.13.2022/Dxj.csv")
#View(dxj.df.4.JA)
ja.full.partial.cricle.count.4.40.subjects <- read.csv("/Users/apple/Desktop/Eric/Research/Karen/Classifier/Data/MostUpdated/JointAttentionRawData/JA.FeatureExtraction..R.Proj./Data/NewRawDataExports_06.13.2022/All/Subjects.With.ExtractedFeatures/FinalRes/ja.full.partial.cricle.count.df.4.all.subjects.csv", row.names = 1)

dxj.df.4.JA$SubjectID <- 
  toupper(dxj.df.4.JA$SubjectID)
ja.full.partial.cricle.count.4.40.subjects$SubjectID <- 
  toupper(ja.full.partial.cricle.count.4.40.subjects$SubjectID)

ja.full.partial.cricle.count.df.4.all.subjects.with.Dxj <- 
  merge(x = ja.full.partial.cricle.count.4.40.subjects, y = dxj.df.4.JA, by = "SubjectID", all.x = TRUE)
#View(ja.full.partial.cricle.count.df.4.all.subjects.with.Dxj)

length(intersect(ja.full.partial.cricle.count.4.40.subjects$SubjectID, dxj.df.4.JA$SubjectID))

#write.csv(ja.full.partial.cricle.count.df.4.all.subjects.with.Dxj, file = "/Users/apple/Desktop/Eric/Research/Karen/Classifier/Data/MostUpdated/JointAttentionRawData/JA.FeatureExtraction..R.Proj./Data/NewRawDataExports_06.13.2022/All/Subjects.With.ExtractedFeatures/FinalRes/ja.full.partial.cricle.count.df.4.all.subjects.with.Dxj.csv")
#save(ja.full.partial.cricle.count.df.4.all.subjects.with.Dxj, file = "/Users/apple/Desktop/Eric/Research/Karen/Classifier/Data/MostUpdated/JointAttentionRawData/JA.FeatureExtraction..R.Proj./Data/NewRawDataExports_06.13.2022/All/Subjects.With.ExtractedFeatures/FinalRes/ja.full.partial.cricle.count.df.4.all.subjects.with.Dxj")
```



















